---
title: "Less 9 W4 Assignment"
author: "Felix m0wlwurf"
date: "7 12 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Idea of App

- short App to showcase the *shiny* skills acquired in this course
- this app will allow the user to set a Value for X using an interactive slider
- for a given X, the probability p(X>x) will be calculated using standard normal distribution
- The App will also visualize X and the distribution function

## Deployment of APP

- App is hosted on *shinyapps.io*
- Link: https://m0wlwurf.shinyapps.io/Less9W4PA_V1/


## Code of server-portion:

```{r ui, echo=TRUE}
server <- function(input, output) {

    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        p <- seq(-5, 5, .1)
        y <- dnorm(p)
        # draw the histogram with the specified number of bins
        plot(p, y, type = "l", xlab = "X", ylab = "Probability Density")
        abline(v = input$x, col = "red")
    })
    output$CumulDist <- renderText(pnorm(input$x))
}
```

## Thank you! :-)

Seriously.. how you gonna fill 5 pages?



